---
title: "STAT 244-SC"
format: html
---

### 🔍 Final Project: Predicting Customer Churn with Logistic and LASSO Regression

This project uses machine learning to address a core economic problem: customer retention. I built logistic and LASSO regression models to predict whether a bank customer will churn based on features like balance, age, activity status, and gender. Using 10-fold cross-validation and ROC-AUC for evaluation, I compared model performance and explored how LASSO can select the most economically meaningful predictors. The results provide actionable insights for firms aiming to reduce churn and improve customer lifetime value.


```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
library(readr)
library(purrr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(mosaic)
library(gmodels)
library(Sleuth3)
```


```{r}
data <- read.csv('Bank Customer Churn Prediction.csv')
head(data)
```

```{r}
data %>%
  ggplot(aes(x = churn, fill = country)) + 
  geom_bar(position = "dodge") +
  labs(x = 'Churn?', y = 'Counts', fill = 'Country') + 
  scale_fill_manual(values = c("steelblue", "lightblue", "darkblue")) + 
  theme_classic()
```

